Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-03-27 write-up/fda-recurrent-supplement.tex
Fixed all simulation tables. now onto adding the aic check on delta and then computation

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate} \\ \cline{3-6}
$\Delta=$ & & 0.5 & 1 & 2 & 4 \\ \hline
\multirow{3}{*}{26} & MISE & $5.9 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.6 \times 10^{-2}$ & $7.4 \times 10^{-2}$ \\
 & Variance & $1.3 \times 10^{-2}$ & $1.6 \times 10^{-2}$ & $12.4 \times 10^{-2}$ & $3.6 \times 10^{-2}$ \\
  & P-MISE & $7.1 \times 10^{-2}$ & $7.3 \times 10^{-2}$ & $7.8 \times 10^{-2}$ & $8.8 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{29} & MISE & $6.9 \times 10^{-2}$ & $7.0 \times 10^{-2}$ & $7.1 \times 10^{-2}$ & $7.8 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.4 \times 10^{-2}$ \\
  & P-MISE & $7.5 \times 10^{-2}$ & $7.5 \times 10^{-2}$ & $7.7 \times 10^{-2}$ & $8.4 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{32} & MISE & $8.1 \times 10^{-2}$ & $8.0 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.7 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.4 \times 10^{-2}$ & $1.9 \times 10^{-2}$ & $3.3 \times 10^{-2}$ \\
  & P-MISE & $8.1 \times 10^{-2}$ & $8.0 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.7 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{35} & MISE & $9.0 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $9.2 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.2 \times 10^{-2}$ & $3.0 \times 10^{-2}$ \\
  & P-MISE & $8.5 \times 10^{-2}$ & $8.2 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.4 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{37} & MISE & $10.3 \times 10^{-2}$ & $10.1 \times 10^{-2}$ & $9.9 \times 10^{-2}$ & $10.1 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.4 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.0 \times 10^{-2}$ \\
  & P-MISE & $9.4 \times 10^{-2}$ & $9.2 \times 10^{-2}$ & $9.0 \times 10^{-2}$ & $9.0 \times 10^{-2}$ \\ \hline
\end{tabular}
\caption{Mean-integrated squared error (MISE), variance, and partial MISE as a function of $\Delta^\star$ and sampling rate when true $\Delta = 32$ minutes.}
\label{tab:appmise}
\end{table}

>>>>

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate (per hour)} \\ \cline{3-6}
$\Delta=$ & & 4.0 & 2.0 & 1.0 & 0.5 \\ \hline
\multirow{3}{*}{26} & MISE & 0.070 & 0.075 & 0.095 & 0.0117 \\
 & Variance & $2.1 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $3.9 \times 10^{-2}$ & $5.8 \times 10^{-2}$ \\
  & P-MISE & 0.085 & 0.091 & 0.115 & 0.141 \\ \hline
\multirow{3}{*}{29} & MISE & 0.072 & 0.076 & 0.093 & 0.111 \\
 & Variance & $1.8 \times 10^{-2}$ & $2.3 \times 10^{-2}$ & $3.4 \times 10^{-2}$ & $5.0 \times 10^{-2}$ \\
  & P-MISE & 0.079 & 0.083 & 0.101 & 0.121 \\ \hline
\multirow{3}{*}{32} & MISE & 0.076 & 0.079 & 0.095 & 0.109 \\
 & Variance & $1.5 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.2 \times 10^{-2}$ & $4.6 \times 10^{-2}$ \\
  & P-MISE & 0.076 & 0.079 & 0.095 & 0.109 \\\hline
\multirow{3}{*}{35} & MISE & 0.083 & 0.085 & 0.099 & 0.114 \\
 & Variance & $1.4 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.2 \times 10^{-2}$ & $4.7 \times 10^{-2}$ \\
  & P-MISE & 0.081 & 0.083 & 0.096, & 0.110 \\\hline
\multirow{3}{*}{37} & MISE & 0.091 & 0.092 & 0.106 & 0.117 \\
 & Variance & $1.5 \times 10^{-2}$ & $2.4 \times 10^{-2}$ & $3.4 \times 10^{-2}$ & $5.0 \times 10^{-2}$ \\
  & P-MISE & 0.088 & 0.089 & 0.102 & 0.112 \\\hline
\end{tabular}
\caption{Mean-integrated squared error (MISE), variance, and partial MISE as a function of $\Delta^\star$ and sampling rate when true $\Delta = 32$ minutes.
% exponential EXAMPLE
}
\label{tab:appmise}
\end{table}

### 2023-03-27 write-up/fda-recurrent.tex
Fixed all simulation tables. now onto adding the aic check on delta and then computation

\begin{table}[!th]
\begin{tabular}{c | p{2cm} p{2cm} p{2cm} p{2cm} p{2cm}}
& \multicolumn{4}{c}{Sampling rate (per)} \\ \cline{2-6}
 & X1 & X2 & X3 & X4 & X5 \\ \hline
SubS. Variance & - & $1.2 \times 10^{-5}$ & $2.0 \times 10^{-5}$ & $3.5 \times 10^{-5}$ & $8.6 \times 10^{-5}$  \\
Variance & $1.3 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.1 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $3.8 \times 10^{-2}$\\
Squared Bias & $6.3 \times 10^{-2}$ & $6.0 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.7 \times 10^{-2}$   \\
MISE & $7.6 \times 10^{-2}$  & $7.5 \times 10^{-2}$  & $8.2 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $1.1 \times 10^{-1}$ \\
RMISE & -  & 0.99  & 1.08 & 1.16 & 1.39 \\ \hline
Avg. runtime (secs) & 356 & 108 & 51 & 24 & 17 \\ \hline
SubS. variance & - & $2.7 \times 10^{-5}$ & $5.1 \times 10^{-5}$ & $5.7 \times 10^{-5}$ & $7.5 \times 10^{-5}$  \\
Variance & $3.7 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $2.8 \times 10^{-2}$ & $3.3 \times 10^{-2}$ &  $3.8 \times 10^{-2}$\\
Squared Bias & $3.5 \times 10^{-2}$ & $3.6 \times 10^{-2}$ & $3.4 \times 10^{-2}$ & $3.3 \times 10^{-2}$ & $3.1 \times 10^{-2}$ \\
MISE & $7.2 \times 10^{-2}$ & $6.3 \times 10^{-2}$ & $6.2 \times 10^{-2}$ & $6.6 \times 10^{-2}$ & $6.9 \times 10^{-2}$ \\
RMISE & -  & 0.87  & 0.86 & 0.92 & 0.96 \\ \hline
Avg. runtime (secs) & 1084 & 208 & 93 & 47 & 30 \\ \hline
\end{tabular}
\caption{Mean-integrated squared error, variance, squared bias, and subsampling (SubS) variance for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}

@@

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate} \\ \cline{3-6}
$\Delta=$ & & 0.5 & 1 & 2 & 4 \\ \hline
\multirow{3}{*}{26} & MISE & 0.400 & 0.404 & 0.409 & 0.413 \\
 & Variance & $1.1 \times 10^{-2}$ & $1.3 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $1.9 \times 10^{-2}$ \\
  & P-MISE & 0.225 & 0.229 & 0.233 & 0.239 \\ \hline
\multirow{3}{*}{29} & MISE & 0.240 & 0.243 & 0.244 & 0.251 \\
 & Variance & $9.2 \times 10^{-3}$ & $1.1 \times 10^{-2}$ & $1.2 \times 10^{-2}$ & $1.8 \times 10^{-2}$ \\
  & P-MISE & 0.107 & 0.109 & 0.111 & 0.117 \\ \hline
\multirow{3}{*}{32} & MISE & 0.105 & 0.103 & 0.103 & 0.105 \\
 & Variance & $8.0 \times 10^{-3}$ & $8.8 \times 10^{-3}$ & $1.0 \times 10^{-2}$ & $1.4 \times 10^{-2}$ \\
  & P-MISE & 0.105 & 0.103 & 0.103 & 0.105 \\\hline
\multirow{3}{*}{35} & MISE & 0.384 & 0.383 & 0.384 & 0.386 \\
 & Variance & $7.0 \times 10^{-3}$ & $7.7 \times 10^{-3}$ & $9.3 \times 10^{-3}$ & $1.1 \times 10^{-2}$ \\
  & P-MISE & 0.273 & 0.270 & 0.269, & 0.269 \\\hline
\multirow{3}{*}{37} & MISE & 0.589 & 0.588 & 0.589 & 0.591 \\
 & Variance & $6.0 \times 10^{-3}$ & $6.5 \times 10^{-3}$ & $7.9 \times 10^{-3}$ & $1.0 \times 10^{-2}$ \\
  & P-MISE & 0.473 & 0.470 & 0.469 & 0.470 \\\hline
\end{tabular}
\caption{Mean-integrated squared error (MISE), variance, and partial MISE as a function of $\Delta^\star$ and sampling rate when true $\Delta = 32$ minutes.}
\label{tab:mise_delta}
\end{table}

>>>>

\begin{table}[!th]
\begin{tabular}{c | p{2cm} p{2cm} p{2cm} p{2cm} p{2cm}}
& \multicolumn{4}{c}{Sampling rate (per hour)} \\ \cline{2-6}
 & 12 & 4.0 & 2.0 & 1.0 & 0.5 \\ \hline
SubS. Variance & - & $1.2 \times 10^{-5}$ & $2.0 \times 10^{-5}$ & $3.5 \times 10^{-5}$ & $8.6 \times 10^{-5}$  \\
Variance & $1.3 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.1 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $3.8 \times 10^{-2}$\\
Squared Bias & $6.3 \times 10^{-2}$ & $6.0 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.7 \times 10^{-2}$   \\
MISE & $7.6 \times 10^{-2}$  & $7.5 \times 10^{-2}$  & $8.2 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $1.1 \times 10^{-1}$ \\
RMISE & -  & 0.99  & 1.08 & 1.16 & 1.39 \\ \hline
Avg. runtime (secs) & 356 & 108 & 51 & 24 & 17 \\ \hline
SubS. variance & - & $2.7 \times 10^{-5}$ & $5.1 \times 10^{-5}$ & $5.7 \times 10^{-5}$ & $7.5 \times 10^{-5}$  \\
Variance & $3.7 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $2.8 \times 10^{-2}$ & $3.3 \times 10^{-2}$ &  $3.8 \times 10^{-2}$\\
Squared Bias & $3.5 \times 10^{-2}$ & $3.6 \times 10^{-2}$ & $3.4 \times 10^{-2}$ & $3.3 \times 10^{-2}$ & $3.1 \times 10^{-2}$ \\
MISE & $7.2 \times 10^{-2}$ & $6.3 \times 10^{-2}$ & $6.2 \times 10^{-2}$ & $6.6 \times 10^{-2}$ & $6.9 \times 10^{-2}$ \\
RMISE & -  & 0.87  & 0.86 & 0.92 & 0.96 \\ \hline
Avg. runtime (secs) & 1084 & 208 & 93 & 47 & 30 \\ \hline
\end{tabular}
\caption{Mean-integrated squared error, variance, squared bias, and subsampling (SubS) variance for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}

@@

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate (per hour)} \\ \cline{3-6}
$\Delta=$ & & 4.0 & 2.0 & 1.0 & 0.5 \\ \hline
\multirow{3}{*}{26} & MISE & 0.390 & 0.395 & 0.397 & 0.413 \\
 & Variance & $5.0 \times 10^{-2}$ & $5.3 \times 10^{-2}$ & $5.5 \times 10^{-2}$ & $6.8 \times 10^{-2}$ \\
  & P-MISE & 0.210 & 0.216 & 0.217 & 0.235 \\ \hline
\multirow{3}{*}{29} & MISE & 0.220 & 0.225 & 0.224 & 0.238 \\
 & Variance & $3.7 \times 10^{-2}$ & $4.4 \times 10^{-2}$ & $4.3 \times 10^{-2}$ & $5.5 \times 10^{-2}$ \\
  & P-MISE & 0.084 & 0.090 & 0.088 & 0.103 \\ \hline
\multirow{3}{*}{32} & MISE & 0.061 & 0.062 & 0.061 & 0.072 \\
 & Variance & $2.7 \times 10^{-2}$ & $2.9 \times 10^{-2}$ & $3.0 \times 10^{-2}$ & $4.2 \times 10^{-2}$ \\
  & P-MISE & 0.061 & 0.062 & 0.061 & 0.072 \\\hline
\multirow{3}{*}{35} & MISE & 0.246 & 0.247 & 0.249 & 0.255 \\
 & Variance & $1.9 \times 10^{-2}$ & $2.1 \times 10^{-2}$ & $2.3 \times 10^{-2}$ & $2.9 \times 10^{-2}$ \\
  & P-MISE & 0.154 & 0.154 & 0.154, & 0.160 \\\hline
\multirow{3}{*}{37} & MISE & 0.360 & 0.359 & 0.353 & 0.361 \\
 & Variance & $2.6 \times 10^{-2}$ & $3.3 \times 10^{-2}$ & $3.7 \times 10^{-2}$ & $4.4 \times 10^{-2}$ \\
  & P-MISE & 0.256 & 0.255 & 0.252 & 0.259 \\\hline
\end{tabular}
\caption{Mean-integrated squared error (MISE), variance, and partial MISE as a function of $\Delta^\star$ and sampling rate when true $\Delta = 32$ minutes.
% SINE EXAMPLE
}
\label{tab:mise_delta}
\end{table}

\subsection{Selection of bandwidth} \label{section:bandwidth}
